Meta-analysis of Fungicide Application Trials for the Management of Powdery Mildew

### 2019-07-26 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd

---
title: Meta-analysis of Fungicide Application Trials for the Management of Powdery Mildew
  in Mungbean.
author: "P. Melloy; E. M. Del Ponte; C. T. Gray; A. H. Sparks;"
date: "24/07/2019"
output: word_document
---

>>>>

---
title: Meta-analysis of Fungicide Application Trials for the Management of Powdery Mildew
  in Mungbean.
author:
  - P. Melloy:
      email: paul.melloy@usq.edu.au
      institute: USQ
      correspondence: true
  - name: E. M. Del Ponte
    institute: UFV
  - name: C. T. Gray
    institute: LaTrobe
  - name: A. H. Sparks
    institute: USQ
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland 4350, Australia
  - LaTrobe: La Trobe University, Melbourne, Victoria 3086, Australia
  - UFV: Universidade Federal de Viçosa, Viçosa, Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::word_document2:
    toc: no
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
---
